### 2023-04-29 main/chapter_theory.tex
incorporate Val's round 2 comments

Supersymmetry is an idea that has been applied to build plausible alternatives
to the Standard Model. and that may explain future experimental discoveries.
Since the main work of this thesis is a search for effects of supersymmetric
phenomena, Section~\ref{sec:theory_susy} discusses supersymmetry and
supersymmetric models.

@@

A convenient first decomposition of the MSSM Lagrangian's parts splits it into
four parts:
\begin{equation}
\mathcal{L}_\mathrm{MSSM} =
\mathcal{L}_\mathrm{SUSY}
+ \mathcal{L}_\mathrm{soft}
+ \mathcal{L}_\mathrm{GF}
+ \mathcal{L}_\mathrm{ghost}
,
\end{equation}
in which
$\mathcal{L}_\mathrm{SUSY}$ is the supersymmetric part,
$\mathcal{L}_\mathrm{soft}$ is the a `softly' breaking part
(which is necessary because supersymmetry is not an unbroken symmetry of
nature),
and
$\mathcal{L}_\mathrm{GF}$ and $\mathcal{L}_\mathrm{ghost}$
are two additions that are necessary for quantization of the
theory~\cite{kuroda1999complete}.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.98\textwidth]{figures/theory_pdg_susy_xsec.pdf}
\caption[
Cross-section scaling of some supersymmetric pair production modes
]{%
Cross-section scaling of some supersymmetric pair production modes
in models similar to the $\twoljets$ C1N2 and GMSB simplified models.
Note the similar scaling parent particle mass  for all gaugino and slepton
production modes shown;
this effect is due to fundamental properties of parton distribution functions
and scattering matrix-elements, and is not unique to supersymmetry.
These cross-sections do not include branching fraction factors, which are
needed to determine both C1N2 and GMSB model cross-sections.
The C1N2 model is wino-like, and the GMSB model is higgsino-like.
This figure is reproduced from~\cite{pdg2022ynf}.
\\[0.4em]
The label `wino` indicates that the gaugino mixtures mostly comprise the
superpartners of the $W$ fields, and `higgsino` indicates that they instead
comprise higgsino fields.
\\[0.4em]
Cross-sections below around $7\,\mathrm{pb}$ are expected to produce no
events in our $139\,\mathrm{fb}^{-1}$ of data.
}
\label{fig:theory_susy_xs}
\end{figure}

Cross-sections for the $\twoljets$ C1N2 and GMSB models are determined by two
factors: production cross-section and the decay branching fraction.
Each process pair-produces some heavy parent particles, so their production
cross-sections scale down with the parent particle mass
as both parton distribution hard-scatter matrix element
are pushed to harder scales.
For mass scale $q$, these three factors combine to an rapidly decaying scaling
of cross-section with parent mass, which goes very roughly like
$\sigma \sim q^{-6}$ in the several-hundred-$\,\eV[G]$ regime.
Production cross-sections for these models are displayed in
Figure~\ref{fig:theory_susy_xs};
in this figure,
cross-sections for the C1N2 model are correspond to those labelled
`$\chargino_1 \neutralino_2$ (wino)', and
cross-sections for the GMSB model are a little smaller, and correspond to those
labelled `$\tilde \chi \tilde \chi$ (higgsino)'.

Typical scenarios studied in $\twoljets$ parent masses ranging from
around $200\,\eV[G]$ to $800\,\eV[G]$ under both of its C1N2 and GMSB models.
The production cross-section for signals from its C1N2 model is
$1800\,\mathrm{fb}$ at $m(\mathrm{parent}) = 200\,\eV[G]$,
and $4.8\,\mathrm{fb}$ at $m(\mathrm{parent}) = 800\,\eV[G]$.
The production cross-section for signals from its GMSB model is
$1300\,\mathrm{fb}$ at $m(\mathrm{parent}) = 200\,\eV[G]$,
and $3.5\,\mathrm{fb}$ at $m(\mathrm{parent}) = 800\,\eV[G]$~\cite{
Fuks:2012qx,Fuks:2013vua}.
These values are rounded to two significant figures.
Cross-section uncertainties are shaded in  Figure~\ref{fig:theory_susy_xs},
but appear very small on its log scale;
the relative uncertainties increase with parent mass from about
$\pm 6\%$ at $m(\mathrm{parent}) = 200\,\eV[G]$.
to about
$\pm 12\%$ at $m(\mathrm{parent}) = 800\,\eV[G]$
in both models.

>>>>

Supersymmetry is an idea that has been applied to build plausible alternatives
to the Standard Model, and which may explain future experimental discoveries.
Since the main work of this thesis is a search for effects of supersymmetric
phenomena, Section~\ref{sec:theory_susy} discusses supersymmetry and
supersymmetric models.

@@

A convenient first decomposition of the MSSM Lagrangian splits it into four
parts:
\begin{equation}
\mathcal{L}_\mathrm{MSSM} =
\mathcal{L}_\mathrm{SUSY}
+ \mathcal{L}_\mathrm{soft}
+ \mathcal{L}_\mathrm{GF}
+ \mathcal{L}_\mathrm{ghost}
,
\end{equation}
in which
$\mathcal{L}_\mathrm{SUSY}$ is the supersymmetric part,
$\mathcal{L}_\mathrm{soft}$ is the a `softly' breaking part
(which is necessary because supersymmetry is not an unbroken symmetry of
nature),
and
$\mathcal{L}_\mathrm{GF}$ and $\mathcal{L}_\mathrm{ghost}$
are two additions that are necessary for quantization of the
theory~\cite{kuroda1999complete}.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.98\textwidth]{figures/theory_pdg_susy_xsec.pdf}
\caption[
Cross-section scaling of some supersymmetric pair production modes
]{%
Cross-section scaling of some supersymmetric pair production modes
in models similar to the $\twoljets$ C1N2 and GMSB simplified models.
Note the similar scaling parent particle mass  for all gaugino and slepton
production modes shown;
this effect is due to fundamental properties of parton distribution functions
and scattering matrix-elements, and is not unique to supersymmetry.
These cross-sections do not include branching fraction factors, which are
needed to determine both C1N2 and GMSB model cross-sections.
The C1N2 model is wino-like, and the GMSB model is higgsino-like.
This figure is reproduced from~\cite{pdg2022ynf}.
\\[0.4em]
The label `wino' indicates that the gaugino mixtures mostly comprise the
superpartners of the $W$ fields, and `higgsino' indicates that they instead
comprise higgsino fields.
\\[0.4em]
Cross-sections below around $7\,\mathrm{pb}$ are expected to produce no
events in our $139\,\mathrm{fb}^{-1}$ of data.
}
\label{fig:theory_susy_xs}
\end{figure}

Cross-sections for the $\twoljets$ C1N2 and GMSB models are determined by two
factors: production cross-section and the decay branching fraction.
Each process pair-produces some heavy parent particles, so their production
cross-sections scale down with the parent particle mass
as both parton distribution functions hard-scatter matrix elements
are pushed to harder scales.
For mass scale $q$, these three factors combine to a rapidly decaying scaling
of cross-section with parent mass, which goes very roughly like
$\sigma \sim q^{-6}$ in the several-hundred-$\,\eV[G]$ regime.
Production cross-sections for these models are displayed in
Figure~\ref{fig:theory_susy_xs};
in this figure,
cross-sections for the C1N2 model correspond to those labelled
`$\chargino_1 \neutralino_2$ (wino)', and
cross-sections for the GMSB model are a little smaller, and correspond to those
labelled `$\tilde \chi \tilde \chi$ (higgsino)'.

Typical scenarios studied in $\twoljets$ have parent particle masses ranging
from around $200\,\eV[G]$ to $800\,\eV[G]$, under both of its C1N2 and GMSB
models.
The production cross-section for signals from its C1N2 model is
$1800\,\mathrm{fb}$ at $m(\mathrm{parent}) = 200\,\eV[G]$,
and $4.8\,\mathrm{fb}$ at $m(\mathrm{parent}) = 800\,\eV[G]$.
The production cross-section for signals from its GMSB model is
$1300\,\mathrm{fb}$ at $m(\mathrm{parent}) = 200\,\eV[G]$,
and $3.5\,\mathrm{fb}$ at $m(\mathrm{parent}) = 800\,\eV[G]$~\cite{
Fuks:2012qx,Fuks:2013vua}.
These values are rounded to two significant figures.
Cross-section uncertainties are shaded in  Figure~\ref{fig:theory_susy_xs},
but appear very small on its logarithmic scale;
the relative uncertainties increase with parent mass from about
$\pm 6\%$ at $m(\mathrm{parent}) = 200\,\eV[G]$.
to about
$\pm 12\%$ at $m(\mathrm{parent}) = 800\,\eV[G]$
in both models.
